Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-09-10 tex/merf/TALMajor/macros.tex
fixed journal tag
fixed journal tag: 2017 not 2018
merf edits done

\submitted[15/10/2017]{TAL~58-03}{R}

@@

\resume{
Les techniques à base de règles pour extraire des entités permettent 
de spécifier les entités souhaitées en utilisant des questions 
de langage naturel, des automates à états finis, des expressions régulières, et des 
instructions d'extraction de données.
Ils nécessitent des expertises en linguistique et en programmation et
ne soutiennent pas l'analyse morphologique d'Arabe.
On présente pour l'Arabe 
un cadre d'extraction d'entité 
renforcé par l'analyse morphologique (\framework). 
Il exige des connaissances be base des 
caractéristiques linguistiques et des expressions régulières, 
et fournit la pouvoire de spécifier de façon interactive 
des fonctionnalités de morphologie et synonymie Arabe,
des types de tag associés avec des expressions régulières, 
et des relations et actions de code définies sur les correspondances de sous-expressions.
\framework construit des entités relationnelles à partir des correspondances
des spécifications.
On évalue \framework avec des études de cas.
Les résultats montrent que \framework nécessite un effort de développement plus courts par rapport aux techniques existantes 
et produit des résultats raisonnablement précis avec une surcharge raisonnable en temps d'exécution.
}

>>>>

%\submitted[15/10/2017]{TAL~58-03}{R}
\journal{TAL. Volume 58 -- n° 3/2017}{1}{25}

@@

\resume{
Les techniques à base de règles pour extraire des entités permettent 
de spécifier les entités souhaitées en utilisant des questions 
de langage naturel, des automates à états finis, des expressions régulières et des 
instructions d'extraction de données.
Ils nécessitent des expertises en linguistique et en programmation, et
ne soutiennent pas l'analyse morphologique de l'arabe.
On présente pour l'arabe 
un cadre d'extraction d'entité 
renforcé par l'analyse morphologique (\framework). 
Il exige des connaissances de base des 
caractéristiques linguistiques et des expressions régulières, 
et fournit la possibilité de spécifier de façon interactive 
des fonctionnalités de morphologie et synonymie arabes,
des types de tag associés avec des expressions régulières, 
et des relations et actions de code définies sur les correspondances de sous-expressions.
\framework construit des entités relationnelles à partir des correspondances
des spécifications.
On évalue \framework avec des études de cas.
Les résultats montrent que \framework nécessite un effort de développement plus court par rapport aux techniques existantes 
et produit des résultats raisonnablement précis avec une surcharge raisonnable en temps d'exécution.
}

### 2018-09-10 tex/merf/TALMajor/results.tex
merf edits done

We evaluated ANGE with
\textit{Musnad Ahmad}, a hadith book, where we constructed an annotated 
golden reference containing 1,865 words.
We evaluated ATEEMA 
with articles from issues of  the Lebanese 
\textit{Al-Akhbar} newspaper where we constructed 
an annotated golden reference containing 1,677 words. 
For the genealogical tree extraction we used 
an extract from the Genesis biblical text with 1,227 words.
Finally, we used an annotated article from the Lebanese \textit{Assafir}
newspaper with 1,399 words to evaluate the NUMNORM case study
\footnote{Available at \url{http://www.assafir.com} and 
\url{http://www.al-akhbar.com}.}. 
%
In the online appendix\footnote{Available at ~\url{http://research-fadi.aub.edu.lb/pdfs/merfappendix.pdf}.},we report on eight additional \framework case studies.
Manual annotators inspected the outcome and provided corrections where tools 
made mistakes.
The corrections form the manual gold annotation that we compared against.

@@

Table~\ref{tab:results} reports the development time,
extraction runtime, recall and precision 
of the output MRE tags, 
the size of the task in lines of code or in number of \framework rules, 
for both the standalone task specific and the \framework implementations.
The development time measures the time required for 
developing the case study.
For instance, ANGE~\cite{ZaMaFlairs2012HadithBio} required two 
months of development by a research assistant with six and 14 hours of 
course work and teaching duties, respectively.
Recall refers to the fraction of the entities correctly detected against the
total number of entities. 
Precision refers to the fraction of correctly
detected entities against the total number of extracted entities.

>>>>

We evaluated ANGE with \textit{Musnad Ahmad}, a hadith book, where we constructed an annotated golden reference containing 1,865 words.
We evaluated ATEEMA with articles from issues of  the Lebanese \textit{Al-Akhbar} newspaper where we constructed an annotated golden reference containing 1,677 words. 
For the genealogical tree extraction we used an extract from the Genesis biblical text with 1,227 words.
Finally, we used an annotated article from the Lebanese \textit{Assafir} newspaper with 1,399 words to evaluate the NUMNORM case study\footnote{Available at~\url{http://www.assafir.com} and 
\url{http://www.al-akhbar.com}.}. 
%
In the online appendix\footnote{Available at~\url{http://research-fadi.aub.edu.lb/pdfs/merfappendix.pdf}.}, we report on eight additional \framework case studies.
Manual annotators inspected the outcome and provided corrections where tools 
made mistakes.
The corrections form the manual gold annotation that we compared against.

@@

Table~\ref{tab:results} reports the development time,
extraction runtime, recall and precision 
of the output MRE tags, 
the size of the task in lines of code or in number of \framework rules, 
for both the standalone task specific and the \framework implementations.
The development time measures the time required for 
developing the case study.
For instance, ANGE~\cite{ZaMaFlairs2012HadithBio} required two 
months of development by a research assistant with 6 and 14 hours of 
course work and teaching duties, respectively.
Recall refers to the fraction of the entities correctly detected against the
total number of entities. 
Precision refers to the fraction of correctly
detected entities against the total number of extracted entities.
